Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries

### 2024-05-01 paper.qmd
adding references using bibtex

---
title: "Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries"
author: "Vincent Xie"
toc: false
number-sections: false
execute:
    echo: false
highlight-style: pygments
format: 
  html: 
    code-fold: true
    html-math-method: katex
  pdf: 
    fontsize: 12pt
    geometry: 
      - top=30mm
      - left=20mm
header-includes:
  - \usepackage{setspace}
  - \doublespacing
##  docx: default
---
```{python}
# Packages
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import statsmodels.api as sm
from scipy.stats import chi2_contingency
import numpy as np
import warnings

@@

# Websites for reference

+ https://pubmed.ncbi.nlm.nih.gov/30452873/
+ https://pubmed.ncbi.nlm.nih.gov/30697503/
+ https://journals.sagepub.com/doi/pdf/10.1177/0363546518808499

>>>>

---
title: "Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries"
author: "Vincent Xie"
bibliography: bibliography.bib
toc: false
number-sections: false
execute:
    echo: false
highlight-style: pygments
format: 
  html: 
    code-fold: true
    html-math-method: katex
  pdf: 
    fontsize: 12pt
    geometry: 
      - top=30mm
      - left=20mm
header-includes:
  - \usepackage{setspace}
  - \doublespacing
##  docx: default
---
```{python}
# Packages
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import statsmodels.api as sm
from scipy.stats import chi2_contingency
import numpy as np
import warnings

@@

# References

@article{Mack2018,
  author = {Mack, Callie D. and Solomon, Gary and Covassin, Tracey and Theodore, Nicholas and Cárdenas, Javier and Sills, Allen},
  title = {Higher Rates of Lower Extremity Injury on Synthetic Turf Compared With Natural Turf Among National Football League Athletes: Epidemiological Confirmation of a Biomechanical Hypothesis},
  journal = {American Journal of Sports Medicine},
  year = {2018},
  volume = {46},
  number = {12},
  pages = {2781--2789},
  doi = {10.1177/0363546518808499}
}

@article{Haider2018,
  author = {Haider, Syed and Kaye-Kauderer, Halley P. and Maniya, Akbar Y. and Dai, Jennifer B. and Li, Adam Y. and Post, Alexander F. and Sobotka, Stanislaw S. and Adams, Ryan and Gometz, Alex and Lovell, Mark R. and Choudhri, Tanvir F.},
  title = {Does the Environment Influence the Frequency of Concussion Incidence in Professional Football?},
  journal = {Cureus},
  year = {2018},
  volume = {10},
  number = {11},
  pages = {e3627},
  doi = {10.7759/cureus.3627}
}

@article{SAGEArticle2018,
  author = {Author Names},
  title = {Title of the SAGE Journal Article},
  journal = {Journal Name},
  year = {2018},
  volume = {Volume Number},
  number = {Issue Number},
  pages = {Page Range},
  doi = {DOI if available}
}
